---
title: "Week 19 Project"
author: "Divyanshu Kawankar"
date: "12/5/2021"
output:
  pdf_document: default
  html_document: default
---
###Population Scale Analysis

>Q13: Read this file into R and determine the sample size for each genotype and their
corresponding median expression levels for each of these genotypes. Hint: The read.table(),
summary() and boxplot() functions will likely be useful here. There is an example R script
online to be used ONLY if you are struggling in vein. Note that you can find the medium value
from saving the output of the boxplot() function to an R object and examining this object.
There is also the medium() and summary() function that you can use to check your
understanding.
  - Refer to data below

```{r}
library(ggplot2)

gene <- read.table("rs8067378_ENSG00000172057.6.txt")

table(gene$geno)

library(dplyr)

summ <- gene %>% 
  group_by(geno) %>% 
  summarize(mean = mean(exp), median = median(exp), sd = sd(exp))

#median values for A/A, A/G, And G/G respectively
summ$median
```

>Q14: Generate a boxplot with a box per genotype, what could you infer from the relative
expression value between A/A and G/G displayed in this plot? Does the SNP effect the
expression of ORMDL3? Hint: An example boxplot is provided overleaf – yours does not need
to be as polished as this one
  - From the relative expression values between A/A and G/G we could infer that since they are all expressed in different values, their difference may be a product of being affected by asthma associated SNPs. Thus, we could infer that SNP could effect the expression of ORMDL3.

```{r}
library(ggplot2)

library(dplyr)

ggplot(gene) + aes(x=geno,y=exp, fill=geno) +
  geom_boxplot(notch=TRUE) 
```

